Garbage Collection Evaluation Infrastructure for the Cog VM

### 2018-06-13 paper.tex
c

\begin{code}
benchAnalysisPyramid
	mooseModel overviewPyramidMetrics.

benchAnalysisSymbol
	mooseModel allMethods symbolsUsedInName

benchAnalysisDeprecation
	mooseModel allModelClasses select: [ :each |
    		(each isAnnotatedWith: 'Deprecated') and: [ each clientTypes notEmpty ] ].
\end{code}

@@

\begin{code}
benchRelease
	mooseModel := nil.
	allProperties := nil.
	3 timesRepeat: [Smalltalk garbageCollect].
\end{code}

@@

>>>>

\begin{code}
GCMooseBench >> benchAnalysisPyramid
	mooseModel overviewPyramidMetrics.

GCMooseBench >> benchAnalysisSymbol
	mooseModel allMethods symbolsUsedInName

GCMooseBench >> benchAnalysisDeprecation
	mooseModel allModelClasses select: [ :each |
    		(each isAnnotatedWith: 'Deprecated') and: [ each clientTypes notEmpty ] ].
\end{code}

@@

\begin{code}
GCMooseBench >> benchRelease
	mooseModel := nil.
	allProperties := nil.
	3 timesRepeat: [Smalltalk garbageCollect].
\end{code}

@@

I think we show exec time, full gc time, scavenge time, compaction time.
